Adapting toolmark based chumbley score to bullets

### 2017-09-25 doc/aboutme.Rmd
.

## R Markdown

Toolmarks:

@@

@@

@@

>>>>

## Toolmarks

@@

```
## Bullets

@@

WO 320 wv 50
```{r echo=FALSE}
a<- matrix(NA, ncol = 3, nrow = 2)
bullet.falsepositive<- data.frame(a)
colnames(bullet.falsepositive)<- c("Classification", "FALSe", "TRUe")
bullet.falsepositive$Classification<- c("FALSe", "TRUe")
bullet.falsepositive$FALSe<- c(77564,412)
bullet.falsepositive$TRUe<- c(4022,674)
bullet.falsepositive

```
Wo 200 WV 50
```{r echo=FALSE}
bullet.falsepositive$FALSe<- c(78817,383)
bullet.falsepositive$TRUe<- c(4004,798)
bullet.falsepositive

```
Wo 80 wv 50
```{r echo=FALSE}
bullet.falsepositive$FALSe<- c(78817,450)
bullet.falsepositive$TRUe<- c(4680,775)
bullet.falsepositive

@@

![](../doc/plots/rate_pt001.png)
